# Name: Nate Edgar
# Date: 8/25/20
# Purpose: Exercise 13



# Install & Put in packages:
```{r}
library(tidyverse)
library(rmapshaper)
library(sf)
```


# Get CONUS state borders from USAboundaries::us_states
```{r}
CONUS_state_borders = 
  USAboundaries::us_states()%>% 
  filter(!state_name %in% c("Hawaii", "Alaska", "Puerto Rico")) %>%
  st_union() %>% 
  st_transform(5070)
```


# Play with both st_simplify and ms_simplify & find the dTolorance and the keep parameters you feel maintain a desired shape and topology
```{r}
stconus100 = CONUS_state_borders %>% 
  st_simplify(dTolerance = 100)

stconus1000 = CONUS_state_borders %>% 
  st_simplify(dTolerance = 1000)

stconus5500 = CONUS_state_borders %>% 
  st_simplify(dTolerance = 5500)

stconus10000 = CONUS_state_borders %>% 
  st_simplify(dTolerance = 10000)

msconus5 = CONUS_state_borders %>% 
  ms_simplify(keep = .05)

msconus10 = CONUS_state_borders %>% 
  ms_simplify(keep = .1)

msconus40 = CONUS_state_borders %>% 
  ms_simplify(keep = .40)

msconus80 = CONUS_state_borders %>% 
  ms_simplify(keep = .80)


#I personally liked using st_simplify more than ms_simplify since this one was easier to undertsand to me & that I like how dTolorance sets the perameter to allow st_simpligy to work and is the distance of points needed to make a map.

```


# Find the number of points in the raw data and in your simplifications using mapview::npts / In your Rmd, create a map for the raw, and each simplified geometry and report the number of points in each
# Plots
```{r}
plot(CONUS_state_borders)
plot(stconus5500)
plot(stconus10000)
mapview::npts(CONUS_state_borders)
mapview::npts(stconus5500)
mapview::npts(stconus10000)

```

```{r}
plot(CONUS_state_borders)
plot(msconus10)
plot(msconus80)
mapview::npts(CONUS_state_borders)
mapview::npts(msconus10)
mapview::npts(msconus80)
```





```{r}
ggplot() + 
  geom_sf(data = CONUS_state_borders) + 
  labs(title = "Full CONUS Map",
       caption = paste("Number of points used = ", mapview::npts(CONUS_state_borders)))
```

```{r}
ggplot() + 
  geom_sf(data = stconus10000) + 
  labs(title = "st_simplify() CONUS Map: dTolerance = 10,000",
       caption = paste("Number of points used = ", mapview::npts(stconus10000)))
```

```{r}
ggplot() + 
  geom_sf(data = msconus10) + 
  labs(title = "ms_simplify() CONUS Map: keep = .1",
       caption = paste("Number of points used = ", mapview::npts(msconus10)))
```

